Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits

### 2022-06-12 04_paper/Draft2.Rmd
commiting minor changes to old draft

However, many observe an unmistakable connection between China’s version of Official Development Assistance (ODA) and its political and material goals. These ambitions include international recognition and closer diplomatic ties with recipients in what China calls “South-South cooperation.” While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility. @mattingly_when_2021 use experiments to demonstrate that investing in both foreign aid and public diplomacy efforts can improve China's image abroad and reduce concerns about the threat it poses. Importantly, both foreign aid and public diplomacy are scarce resources for building bilateral relationships and improving one's image abroad. It is plausible to expect governments find a cluster of foreign countries to be strategically important partners, and to invest in bilateral relationships through aid, mediated public diplomacy, and diplomatic visits.

We conceptualize two distinct but complementary modes of interactions from the face value between foreign aids and media/public diplomacy: secret and open. So, absent traditional modes of transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*

We argue that countries that receive higher media exposure and diplomacy efforts are strategically more important to Beijing, and in turn receive disproportionately larger China’s foreign aid. We tackle this question by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities. Both dimensions are important to build its public diplomacy efforts. These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese official media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. All else equal, we argue that developing countries that receive higher media coverage and diplomatic visit are strategically more important than the others.

To test this expectation, we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy-seeking objectives on the world stage.

This work further helps in dispelling the notion that China purposely engages in development finance in secret. Much to the contrary, China complements its aid giving with visible diplomatic envoys and greater external-facing media coverage. To our understanding, this is the first attempt to use media agenda-setting and public diplomacy to explain Chinese foreign aids allocations. At the end of the day, government-sponsored communication, diplomatic outreach, and financial assistance to developing countries are all crucial to Beijing achieving its foreign policy goals and promoting its soft power.

@@

China's motivations for giving foreign aid to developing countries mirror, in many ways, the motivations of Western donors. While recipient needs, in part, predicate Chinese assistance, so do Beijing's political and economic interests. Evidence suggests that China targets more finance toward poorer countries and does not systematically favor authoritarian over democratic recipients [@dreherEtAl2018]. At the same time, China gives more aid to countries that import more goods from China, while it gives less aid to those that officially recognize Taiwan [@dreherFuchs2015]. Further, China's Official Financing disproportionately goes to countries with more natural resources, greater UN General Assembly voting alignment with Beijing, and with more capacity to repay loans [@dreherEtAl2021].

Two waves of surveys conducted by AidData of policymakers in 126 countries demonstrate the diplomatic impact that these investments have had.^[Reported by AidData ["China's Financial Statecraft: Winning Africa one Yuan at a Time?"](https://www.aiddata.org/blog/chinas-financial-statecraft-winning-africa-one-yuan-at-a-time) on March 22, 2018. Accessed March 3, 2022] Compared to a first survey wave in 2014, responses in 2017 showed an increase in evaluations of China's influence with policymakers in developing countries. It would be naive to suppose this is a side-effect, rather than a goal, of China's development finance and other investments.

If its diplomatic motives for giving aid parallel those of other donor governments, visibility is surely a major concern for Beijing. Visual branding of aid has emerged as a growing concern among donors. The United States Agency for International Development (USAID), for example, cited its "new 'brand identity'" as instrumental in promoting the visibility of 2004-2005 tsunami relief to Indonesia.^[See USAID's resource page on branding: [usaid.gov/branding](https://www.usaid.gov/branding).] A US State Department report from 2004 further claims that better branding contributed to a doubling of favorable attitudes toward the US. Pew Research supports this view, finding that nearly 80$\%$ of Indonesians surveyed "said that post-tsunami aid from the US had improved their impression of America."^[["Does humanitarian aid improve America's image?"](https://www.pewresearch.org/global/2012/03/06/does-humanitarian-aid-improve-americas-image/) Published by Pew Research March 6, 2012. Accessed March 3, 2022.]

Given the diplomatic uses of foreign aid, the obscurity that surrounds Beijing's development finance is all the more puzzling. Unlike Western donors, China does not report its financing activities to an international organization or make its activities visible in an online database. To say transparency is out of character for Beijing is an understatement, but foreign aid is one issue area where transparency would arguably serve China's interests. So why the secrecy?

As @fuchsRudyak2019 point out, the obscurity of China's development finance creates the perception among Western donors that China purposefully keeps its aid giving a secret. But as several scholars note, lack of transparency may have more to do with capacity and logistics than intention.^[See @fuchsRudyak2019 for several related citations.] For many decades, a complex and fractured bureaucracy has orchestrated Beijing's development financing. Only in the past few years, as its goals have become ever loftier, did China establish its first true bilateral aid agency---the China International Development Cooperation Agency (CIDCA). However, while established in 2018, much work remains to consolidate the operation and management of China's bilateral aid.^[See this excellent summary entitled ["The Logic Behind China's Foreign Aid Agency"](https://carnegieendowment.org/2019/05/21/logic-behind-china-s-foreign-aid-agency-pub-79154) by the Carnegie Endowment for International Peace published May 21, 2019. Accessed March 10, 2022.]

Absent transparency in reporting, there are other tools at Beijing's disposal that may complement the diplomatic objectives behind its foreign aid. In this study, we explore the connections between China's bilateral development finance and other, *visible*, activities linked to diplomatic and legitimacy-seeking objectives. We focus in particular on two factors: (1) diplomatic visits from China to developing countries and (2) coverage of developing countries in external-facing media (that is, media coverage intended for foreign, rather than domestic, audiences). We summarize these factors in greater detail in the following sections.

@@

Agenda-setting refers to the ability of media to signal to the public what is important. Media coverage of a foreign country measures how important a country is to its reporting country, in particular, to the public. That is, the public learns the importance of objects based on the amount of coverage that those objects receive. Agenda-setting theory suggests that mass media serve as one of the key sources for public perception of important issues (@mccombs_agenda-setting_1972). More specifically, as @berelson_mass_1966 observe, “The mass media force attention to certain issues. They build up public images of political figures. They are constantly presenting objects suggesting what individuals in the mass should think about, know about, have feelings about” (p. 468). Since their seminal work, hundreds of studies have examined this media effect on the public. The vast majority support this agenda-setting notion (need some more extension or citations here).

Over decades of rich research in agenda-setting, empirical patterns support @cohen_press_1963’s famous notation that the media is “stunningly successful in telling its readers what to think *about*” (p. 13; emphasis added). That is, the salience of news media reports transfers to the perception of issue salience to the public (@mccombs_agenda-setting_1972). Extensive media coverage provides news consumers with salience cues regarding the importance of the political figures or issues, and in turn shape individuals’ perceptions of the relative importance and salience of the issues.

@@

Also, previous findings show the strategic consideration of news editors in considering what international news gets media cover. Not all countries in the world receive equal coverage. In fact, only a small portion of international events can get through the media gatekeepers and get media coverage. While most powerful core states consistently receive higher amounts of coverage from newscasts, small peripheral states remain largely uncovered. @golan_international_2003-1’s study examines how 138 elections held between 1998 and 2000 were covered by the U.S. network television newscasts (ABC, CBS, NBC and CNN). They found that elections in Europe, Asia or the Middle East received substantial coverage than those in Latin America and Africa. A large body of literature has examined the determinants of international news coverage and has identified variables such as geographic locations, cultural proximity, geopolitical position in the world system as key predictors of coverage (@sheafer_relative_2014-1). Hence, if foreign countries receive more media coverage, the increased media salience suggests the salience of the foreign countries to the audiences and the newsworthiness to the news editors.

@@

Hence, while *Xinhua* plays a major role in defining, shaping and projecting China's image, its primary function is to transmit information. It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors. Taking into account the limited space of *Xinhua* to report global affairs, editors’ choices reflect which countries are more than the others to receive media coverage.

@@

Previous sections illustrate media agenda setting as an essential step in a country's public diplomacy process to influence the public's opinion in a second country. For example, building international media outreach to have a space in the global marketplace of ideas are the Chinese government's crucial step to "speak to [foreign] people – and listen to them" (@hoffman_introduction_1968, p. 4). In fact, all public diplomacy programs have a primary responsibility to explain and defend government policies to foreign audience" (@deibel_culture_1976, p. 15).

@@

We have made the case that both state-sponsored media outreach and diplomatic visits have essential implications to sway foreign public opinion. News editors build the credibility of the news agency to transmit information around the globe. High-level officials spend time and resources to visit other countries for economic or security purposes to strengthen their bilateral relationship. Since both approaches involve limited time and resources, we expect that Beijing will choose on whom to cast the spotlight, and whom to visit, strategically. In other words, countries that receive higher state-sponsored media coverage and diplomatic visits are strategically important in the eyes of Beijing. They are in the potential friend circle. While public diplomacy is one way to increase a state’s soft power, in the end, it is intangible power and symbolic. Foreign aid, instead, provides tangible and material support to countries in need. Hence, we expect China to prioritize giving foreign aid to its “friends”---countries where China has developed strong relationships through public diplomacy efforts. This rationale leads to our hypotheses:

> *H1: When developing countries receive more media exposure in *Xinhua*, they are more likely to receive more foreign aid from China.*

@@

To assess complementarities between China's bilateral diplomatic visits and state sponsored media coverage of developing countries with Beijing's bilateral development finance, we combine data from multiple sources. We merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. The full dataset consists of unique recipient-year observations from 2000 to 2014.

@@

Results are shown for `r scales::comma(nrow(dt %>% filter(year!=2000)))` unique recipient-year observations from 2001 to 2014. Multiple imputation for missing values in covariates was done via chaining random forests combined with predictive mean matching, which ensures imputed values do not differ from values already present in the data (such as in the case of a binary variable) and that the conditional distributions have realistic variances.^[For multiple imputation we used the `missRanger` R package. See @stekhovenBuhlmann2011 for more on the method and its robustness relative to other approaches.] Summary statistics are shown the Appendix.

@@

@@

In this study, we tackle this question by considering complementarities between where China gives aid with Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities. These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage.

@@

\captionsetup{labelformat=AppendixTables}
\setcounter{table}{0}

```{r}
dt %>%
  mutate(
    aid = aid / 1000000,
    count = count / 1000,
    trade = trade / 1000000000,
    gdp = gdp / 1000000,
    pop = pop / 1000000
  ) %>%
  summarize(
    across(
      c(aid, count, govt_visits, pmm_fh, gdp:unemp, disaster:dist, trade, atopally),
      list(Mean = mean, Median = median, SD = sd, Min. = min, Max. = max),
      na.rm=T
    ) 
  ) %>%
  pivot_longer(cols = everything()) %>%
  separate(
    col = name,
    into = c(" ", "stat"),
    sep = "_(?=[^_]+$)"
  ) %>%
  mutate(
    value = scales::comma(round(value, 2))
  ) %>%
  pivot_wider(
    values_from = value,
    names_from = stat
  ) %>%
  mutate(
    " " = c(
      "Aid (millions)",
      "Article Mentions (thousands)",
      "Government Visits",
      "Freedom House",
      "GDP (in 100 millions)",
      "Population (in millions)",
      "Unemployment Rate",
      "Disaster Deaths",
      "Civil War",
      "Distance (in kilometers)",
      "Trade (in millions)",
      "Allies"
    )
  ) %>%
  kbl(
    caption = "Summary Statistics (2000-2014)",
    booktabs = T,
    linesep = ""
  )
```

>>>>

However, many observe an unmistakable connection between China's version of Official Development Assistance (ODA) and its political and material goals. These ambitions include international recognition and closer diplomatic ties with recipients in what China calls "South-South cooperation." While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility. So, absent traditional modes of transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*

We tackle this question by considering Chinese media coverage of developing countries intended for foreign audiences and China's bilateral diplomatic activities. These measures capture two distinct but related aspects of China's foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China's development finance complements these goals, we expect greater coverage of a developing country in a Chinese official media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.

To test this expectation, we merge AidData's Chinese development finance dataset with two newly available datasets: (1) AidData's compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation patterns map to China's broader diplomacy and legitimacy-seeking objectives on the world stage.

This work further helps in dispelling the notion that China purposely engages in development finance in secret. Much to the contrary, China's development finance moves in step with visible acts of diplomacy and external-facing media coverage. To our understanding, this is the first attempt to use media agenda-setting and public diplomacy to explain Chinese foreign aid allocations. As we show, government-sponsored communication, diplomatic outreach, and financial assistance to developing countries are all crucial to Beijing achieving its foreign policy goals and promoting its soft power.

@@

China's motivations for giving foreign aid to developing countries mirror, in many ways, the motivations of Western donors. @bermeo2018 provides a recent and authoritative review of the literature on donor objectives, which have historically centered on some combination both of non-development geopolitical and material interests, and of legitimate efforts to address recipient country needs. Beijing's aid giving appears to follow a similarly mixed set of motivations. Studies show that China targets more finance toward poorer countries and does not systematically favor authoritarian over democratic recipients [@dreherEtAl2018]. At the same time, China gives more aid to countries that import more goods from China, while it gives less aid to those that officially recognize Taiwan [@dreherFuchs2015]. Further, China's Official Financing disproportionately goes to countries with more natural resources, greater UN General Assembly voting alignment with Beijing, and with more capacity to repay loans [@dreherEtAl2021].

Two waves of surveys conducted by AidData of policymakers in 126 countries demonstrate the diplomatic impact that these investments have had.[^1] Compared to a first survey wave in 2014, responses in 2017 showed an increase in evaluations of China's influence with policymakers in developing countries. It would be naive to suppose this is a side-effect, rather than a goal, of China's development finance and other investments.

[^1]: Reported by AidData ["China's Financial Statecraft: Winning Africa one Yuan at a Time?"](https://www.aiddata.org/blog/chinas-financial-statecraft-winning-africa-one-yuan-at-a-time) on March 22, 2018. Accessed March 3, 2022

If its diplomatic motives for giving aid parallel those of other donor governments, visibility is surely a major concern for Beijing. Visual branding of aid has emerged as a growing concern among donors. The United States Agency for International Development (USAID), for example, cited its "brand identity" as instrumental in promoting the visibility of 2004-2005 tsunami relief to Indonesia.[^2] A US State Department report from 2004 further claims that better branding contributed to a doubling of favorable attitudes toward the US. Pew Research supports this view, finding that nearly 80$\%$ of Indonesians surveyed "said that post-tsunami aid from the US had improved their impression of America."[^3]

[^2]: See USAID's resource page on branding: [usaid.gov/branding](https://www.usaid.gov/branding).

[^3]: ["Does humanitarian aid improve America's image?"](https://www.pewresearch.org/global/2012/03/06/does-humanitarian-aid-improve-americas-image/) Published by Pew Research March 6, 2012. Accessed March 3, 2022.

Given the diplomatic uses of foreign aid, the obscurity that surrounds Beijing's development finance is all the more puzzling. Unlike Western donors, China does not report its financing activities to an international organization or make its activities visible in an online database. To say transparency is out of character for Beijing is an understatement, but foreign aid is one issue where transparency would arguably serve China's interests. So why the secrecy?

As @fuchsRudyak2019 point out, the obscurity of China's development finance creates the perception among Western donors that China purposefully keeps its aid giving a secret. But as several scholars note, lack of transparency may have more to do with capacity and logistics than intention.[^4] For many decades, a complex and fractured bureaucracy has orchestrated Beijing's development financing. Only in the past few years, as its goals have become ever loftier, did China establish its first true bilateral aid agency---the China International Development Cooperation Agency (CIDCA). However, while established in 2018, much work remains to consolidate the operation and management of China's bilateral aid.[^5]

[^4]: See @fuchsRudyak2019 for several related citations.

[^5]: See this excellent summary entitled ["The Logic Behind China's Foreign Aid Agency"](https://carnegieendowment.org/2019/05/21/logic-behind-china-s-foreign-aid-agency-pub-79154) by the Carnegie Endowment for International Peace published May 21, 2019. Accessed March 10, 2022.

Nonetheless, absent transparency in reporting, it has proved difficult to provide direct confirmation that China's foreign aid is motivated by such public goals as south-south diplomacy and international legitimacy. However, newly available datasets offer an opportunity to empirically probe these motives. In this study, we explore the connections between China's bilateral development finance and critical *visible* activities linked to the diplomatic and legitimacy-seeking objectives scholars attribute to China's international development finance. We focus in particular on two factors: (1) diplomatic visits from China to developing countries and (2) coverage of developing countries in external-facing state-run media.

The details of these factors are covered in greater detail in the following sections. However, to quickly summarize our argument, we believe diplomatic visits and media coverage are important factors for two reasons.

First, they signal the importance of developing countries to Beijing. Just like development finance, diplomatic trips and media coverage are subject to scarcity---the first in terms of limited resources and bandwidth; the second in terms of time dedicated to writing, editing, and publishing content. Within the rationalist framework most often adopted by IR scholars who study international aid, this implies a direct correspondence between the countries that host diplomatic visits and that are subjects of state-sponsored news articles and the importance of developing countries to China. In short, visits and coverage are costly, and they therefore tell us something about which developing countries Beijing values most.

Second, diplomatic visits and state-sponsored media coverage are *visible* acts. Though some diplomatic visits are certainly covert, most are public, even performative displays of the closeness and alignment between host and guest. And media coverage are by their very nature public.

Thus, taken together, diplomatic visits to, and state-run media coverage of, developing countries serve both as signals of the importance of developing countries to Beijing and as visible indicators of the diplomatic and legitimacy-seeking objectives proposed to motivate China's international development finance activities.

@@

Agenda-setting refers to the ability of media to signal to the public what is important. Media coverage of a foreign country measures how important a country is to its reporting country, in particular, to the public. That is, the public learns the importance of objects based on the amount of coverage that those objects receive. Agenda-setting theory suggests that mass media serve as one of the key sources for public perception of important issues (@mccombs_agenda-setting_1972). More specifically, as @berelson_mass_1966 observe, "The mass media force attention to certain issues. They build up public images of political figures. They are constantly presenting objects suggesting what individuals in the mass should think about, know about, have feelings about" (p. 468). Since their seminal work, hundreds of studies have examined this media effect on the public. The vast majority support this agenda-setting notion (need some more extension or citations here).

Over decades of rich research in agenda-setting, empirical patterns support @cohen_press_1963's famous notation that the media is "stunningly successful in telling its readers what to think *about*" (p. 13; emphasis added). That is, the salience of news media reports transfers to the perception of issue salience to the public (@mccombs_agenda-setting_1972). Extensive media coverage provides news consumers with salience cues regarding the importance of the political figures or issues, and in turn shape individuals' perceptions of the relative importance and salience of the issues.

@@

Also, previous findings show the strategic consideration of news editors in considering what international news gets media cover. Not all countries in the world receive equal coverage. In fact, only a small portion of international events can get through the media gatekeepers and get media coverage. While most powerful core states consistently receive higher amounts of coverage from newscasts, small peripheral states remain largely uncovered. @golan_international_2003-1's study examines how 138 elections held between 1998 and 2000 were covered by the U.S. network television newscasts (ABC, CBS, NBC and CNN). They found that elections in Europe, Asia or the Middle East received substantial coverage than those in Latin America and Africa. A large body of literature has examined the determinants of international news coverage and has identified variables such as geographic locations, cultural proximity, geopolitical position in the world system as key predictors of coverage (@sheafer_relative_2014-1). Hence, if foreign countries receive more media coverage, the increased media salience suggests the salience of the foreign countries to the audiences and the newsworthiness to the news editors.

@@

Hence, while *Xinhua* plays a major role in defining, shaping and projecting China's image, its primary function is to transmit information. It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors. Taking into account the limited space of *Xinhua* to report global affairs, editors' choices reflect which countries are more than the others to receive media coverage.

@@

Previous sections illustrate media agenda setting as an essential step in a country's public diplomacy process to influence the public's opinion in a second country. For example, building international media outreach to have a space in the global marketplace of ideas are the Chinese government's crucial step to "speak to [foreign] people -- and listen to them" (@hoffman_introduction_1968, p. 4). In fact, all public diplomacy programs have a primary responsibility to explain and defend government policies to foreign audience" (@deibel_culture_1976, p. 15).

@@

We have made the case that Beijing's international development finance serves, among a diverse set of objectives, the promotion of diplomatic ties abroad and a particular image of China and its role in the international community. But, we have also highlighted a puzzle. If policymakers in China seek to support these goals with foreign aid, why the lack of transparency about where and how much China spends on development finance? We contend that limited transparency is much less a purposeful choice but a product of a complex bureaucracy that makes data reporting logistically impractical. Nonetheless, if China's foreign aid does indeed support this pair of objectives we should expect its giving to parallel other activities that are visible acts of diplomacy and image building.

In this paper, we focus on the special roles that state-sponsored media outreach and diplomatic visits have in promoting international legitimacy and stronger diplomatic ties with "southern" country governments. In addition to being visible actions taken by Beijing to support these goals, envoys and media coverage are also costly due to limited resources in terms of time and funding. We expect, therefore, that Beijing will choose on whom to cast the spotlight, and whom to visit, strategically. In particular, countries that receive higher state-sponsored media coverage and that host a greater number of diplomatic visits should be strategically important in the eyes of Beijing.

However, while public diplomacy is one way to increase a state's soft power, in the end, visits and media are fleeting and symbolic. To reinforce the objectives pursued through these visible acts of diplomacy, we argue that Beijing uses other tools, such as foreign aid, to provide tangible and material support to important countries. Hence, we expect that to the extent that Beijing uses foreign aid as a tool in support of these particular foreign policy goals, we should see Chinese development finance parallel these different but complementary activities. This rationale leads to our hypotheses:

> *H1: When developing countries receive more media exposure in* Xinhua*, they are more likely to receive more foreign aid from China.*

@@

To assess complementarities between China's bilateral diplomatic visits and state sponsored media coverage of developing countries with Beijing's bilateral development finance, we combine data from multiple sources. We merge AidData's Chinese development finance dataset [@dreherEtAl2021 and @dreherEtAl2022] with two newly available datasets: (1) AidData's compiled yearly counts of bilateral official diplomatic visits from China [@aidData2021] and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research [-@cline2022]. The full dataset consists of unique recipient-year observations from 2000 to 2014.[^6]

[^6]: Version 1.0 of the Chinese development finance dataset may be obtained at: <http://aiddata.org/data/chinese-global-official-finance-dataset>. The data on China's public diplomacy can be obtained at: <http://china-dashboard.aiddata.org/>. Finally, the Archer portal used to access extracted features in the Global News Index at the Cline Center can be found at: <https://databank.illinois.edu/datasets/IDB-2179938>.

@@

Results are shown for `r scales::comma(nrow(dt %>% filter(year!=2000)))` unique recipient-year observations from 2001 to 2014. Multiple imputation for missing values in covariates was done via chaining random forests combined with predictive mean matching, which ensures imputed values do not differ from values already present in the data (such as in the case of a binary variable) and that the conditional distributions have realistic variances.[^7] Summary statistics are shown the Appendix.

[^7]: For multiple imputation we used the `missRanger` R package. See @stekhovenBuhlmann2011 for more on the method and its robustness relative to other approaches.

@@

```{=tex}

@@

In this study, we tackle this question by considering complementarities between where China gives aid with Chinese media coverage of developing countries intended for foreign audiences and China's bilateral diplomatic activities. These measures capture two distinct but related aspects of China's foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China's development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. To test this expectation we merge AidData's Chinese development finance dataset with two newly available datasets: (1) AidData's compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation patterns map to China's broader diplomacy and legitimacy seeking objectives on the world stage.

@@

```{=tex}
\captionsetup{labelformat=AppendixTables}
\setcounter{table}{0}
```
```{r}
dt %>%
  mutate(
    aid = aid / 1000000,
    count = count / 1000,
    trade = trade / 1000000000,
    gdp = gdp / 1000000,
    pop = pop / 1000000
  ) %>%
  summarize(
    across(
      c(aid, count, govt_visits, pmm_fh, gdp:unemp, disaster:dist, trade, atopally),
      list(Mean = mean, Median = median, SD = sd, Min. = min, Max. = max),
      na.rm=T
    ) 
  ) %>%
  pivot_longer(cols = everything()) %>%
  separate(
    col = name,
    into = c(" ", "stat"),
    sep = "_(?=[^_]+$)"
  ) %>%
  mutate(
    value = scales::comma(round(value, 2))
  ) %>%
  pivot_wider(
    values_from = value,
    names_from = stat
  ) %>%
  mutate(
    " " = c(
      "Aid (millions)",
      "Article Mentions (thousands)",
      "Government Visits",
      "Freedom House",
      "GDP (in 100 millions)",
      "Population (in millions)",
      "Unemployment Rate",
      "Disaster Deaths",
      "Civil War",
      "Distance (in kilometers)",
      "Trade (in millions)",
      "Allies"
    )
  ) %>%
  kbl(
    caption = "Summary Statistics (2000-2014)",
    booktabs = T,
    linesep = ""
  )
```
